---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PEMcollectr)
```

## Running the app from the installed package

```r
run_PEM_app(local = FALSE)
```


## Data Validation

The core data validation functions are function factories and meant to be applied 
to a single column of data or vector.

```{r}
validate_character()(LETTERS)
```


The function factories must return  a list with status (TRUE/FALSE) and an
informative message. If the validation passes, `''` is returned.

```{r}
validate_integer()(LETTERS)
```

You can apply multiple validations to a single vector by passing the 
functions in the `...` argument. The messages are combined collapsed into a 
single message with ";".

```{r}
validate_data(x = LETTERS, validate_integer(), validate_float())
```

Apply all tests to an sf data.frame object.

```r
validate_PEM_data(PEMPoints, f = validate_field_points_data)
```

## Data

Categories of data are provided as functions that produce named vectors.

```{r}
point_type()
```

## Postgresql DB Interactions

Connect to PG database with preferred functions for developing locally or 
for deployment. Set the `PGHOST`, `PGUSER`, `PGPASSWORD` environment 
variables to authenticate.

```r
con <- connect_pg(dbname = 'PEM')
```

Append data to a table.

```r
append_db(con, PEMPoints, 'staging.staging.field_points_data')
```

